---
title: "General Assembly DSI Project 4 in R"
output: html_notebook
author: Isaac Moore
---

```{r}
setwd("~/Google Drive/data_science/general_assembly/Projects/DSI_SM_Project4")
```
  
Load the tidyverse and other libraries
```{r}
library("tidyverse")
library("rvest")
require(scales)
```
  

```{r}
test <- read_html("https://www.indeed.com/jobs?q=data+analyst&l=Los+Angeles%2C+CA") %>%
        html_nodes(xpath = '//*[row result"]') %>% 
        html_text()
test

# cast <- lego_movie %>%
#   html_nodes("#titleCast .itemprop span") %>%
#   html_text()
# cast
```

Using the example dataset provided.

```{r}
raw_data <- read_csv("indeed-scraped-job-postings.csv")
df <- raw_data
head(df)

```


```{r}
nrow(df)
ncol(df)
```

```{r}
df %>% filter(!is.na(parsed_salary)) %>%
        group_by(city) %>% 
        summarise(mean_salary = mean(parsed_salary))
```

```{r}
# avg_salary <- mean(subset(df, !is.na(parsed_salary))$parsed_salary)
a <- which(is.na(df$parsed_salary))
df[a, ]
```

```{r}
# weekdays <- 52*5
# salary <- (650+900) / 2
# fill_salary <- weekdays * salary
# df[a, ]$parsed_salary <- fill_salary
```

Omit na's from the dataframe.
```{r}
df2 <- df %>% na.omit()
nrow(df2)
ncol(df2)
```
Not many rows dropped.

```{r}
df2 %>% group_by(city) %>% 
        summarise(mean_salary = mean(parsed_salary))
```

Compare salarys by removing duplicate rows in the dataframe.
```{r}
df2 %>% distinct() %>% group_by(city) %>% summarise(mean_salary = mean(parsed_salary))
```

remove duplicate rows
```{r}
df3 <- df2 %>% distinct()
nrow(df3)
ncol(df3)
```
dropped a lot of rows!

### Checking the descrpencies between Austin/Seattle and the other states.
```{r}
df3%>% filter(city == "Austin")
```
Monthly salaries are mixed in with Yearly salaries. 


*I'll make a function for any parsed salary that is less than $15,000 to multiply by 12 to calculate yearly salary.*
```{r, echo=TRUE}
year_salary <- function(x){
        # Take in a vector (column) and iterate through each element in the vector.
        out <- 0
        vec <- c()
        for(i in x){
                if(i <= 15000){
                        vec <- c(vec,(i * 12))
                } else{
                        vec <- c(vec, i)
                }
        }
        return(vec)
}
df3$wage <- year_salary(df3$parsed_salary)
```


```{r}
df3 %>% select(parsed_salary, wage)
```

```{r}
df3 %>% group_by(city) %>% summarise(avg_salary = mean(wage))
```


```{r}
avg_salary_city <- df3 %>%
        group_by(city) %>% 
        summarise(mean_salary = mean(wage))
# avg_salary_city
ggplot(avg_salary_city, aes(city, mean_salary)) + 
        geom_bar(stat="identity") + 
        coord_flip() + 
        scale_y_continuous(labels = comma) + 
        labs(title="Average salaries per city", y="Average Salary", x="City")
```

```{r}
df3 %>% ggplot(aes(city, wage)) + 
        geom_boxplot() + 
        scale_y_continuous(labels = comma) + 
        labs(title="Distribution of salaries per city", x="City", y="Yearly Salary")
# boxplot(df2$parsed_salary ~ df2$city)
```

```{r}
# df3 %>% ggplot(aes(wage)) + 
#         geom_histogram(binwidth = 12) + 
#         # scale_x_continuous(labels = comma)
hist(df3$wage, breaks = 9, xlab = "Yearly Salary", main = "Frequency of Yealry Salaries")
```


```{r}
summary(df3$wage)
```

### Lets build a model to prdict whether the salary will be high or low based off of the City.  
**We want to predict a binary variable - whether the salary was low or high. Compute the median salary and create a new binary variable that is true when the salary is high (above the median)**
```{r}
#df3$above_median <- l
```

Find which columns are above the median
```{r}
#which(df3$wage > median(df3$wage))
above_median <- function(x){
        med <- median(df3$wage)
        if(x > med){
                return(1)
        } else {
                return(0)
        }
}
df3$above_median <- sapply(df3$wage, above_median)
table(df3$above_median)
```

Thought experiment: What is the baseline accuracy for this model?
```{r}
mean(df3$above_median)
```

Create a Logistic Regression model to predict High/Low salary using statsmodel. Start by ONLY using the location as a feature. Display the coefficients and write a short summary of what they mean.
```{r}
model <- glm(formula = "above_median ~ city", family = binomial(link = "logit"), data = df3)
summary(model)
```






